---
title: "p8105_hw5_sl4269"
author: "Steven Lawrence"
date: "November 4, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))


```
#Problem 1

```{r}

df<-tibble(
num_vec <- c(1,2,3,NA,5),
cha_vec <- c("a","b",NA,"d","c"))


rep_miss<- function(x){
  
  if(is.numeric(x)){
    x[is.na(x)] = mean(x,na.rm = T)
  
  } else if (is.character(x)){
   x[is.na(x)] = "virginica"
  } else {
    stop("should be numeric or character")
  }
  
  x
  
}
 map_dfr( df, rep_miss ) #%>% map_dfr(rbind)

output




```

```{r}
iris_with_missing %>% map_dfr(rep_miss)


```

#Problem 2

```{r}
 
file_coerce <- function(x){
  read_csv(x, col_names = c("subject Id", "control arm"))
}

map(list.files("./data/"), file_coerce)
```


#Problem 3

```{r}

sim_fun <- function(n = 30, beta1 , beta0 = 2,sig2 = 50){

  x = rnorm(n ,0,1)
  e = rnorm(n, 0, sig2)
  y = beta0 + beta1*x + e
  
  linreg<-lm(y ~ x)

  return(tibble(
  b1h = linreg$coefficients[2],
  pval= summary(linreg)$coefficients[8],
  beta1 = beta1
  ))
  
}

trials <- function(x, func, beta1 ){

1:x %>% map(function(x) func(beta1 = beta1)) %>% map_dfr(rbind) 
  
}



Beat1_data<-0:6 %>% 
  map(function(x) trials(10000, sim_fun, x)) %>% 
  map_dfr(rbind)

```

##Proportion of hpothesis test results.

In this proportion bar plot we see that as the beta1or the coefficient of the x value increase there is an increase in rejecting the null.  This means that as beta 1 increases the power of this test increases.  Therefore for small sample sizes there needs to be a strong beta 1 effect on x in order to attain enough power.

```{r}
   

   Beat1_data %>%  mutate(beta1 = as.numeric(beta1),
           beta1 = as.factor(beta1),
           null_rejected = case_when(
             pval < 0.05 ~ "reject",
             pval >= 0.05 ~ "fail to reject"
           )) %>% 
    group_by(beta1, null_rejected) %>% 
    summarize(
      obs = n()
    ) %>% 
  ggplot(aes(x = beta1, y =obs))+ 
   geom_bar( aes(#color = null_rejected, 
                 fill = factor(null_rejected)
                 ),
    stat = "identity", position = position_stack()
    )+
  scale_fill_discrete("Hypothesis Result")+
  ggtitle("Proportion of Times The Null was Rejected")

  



```

##Scatter plot of mean beta 1 hat

In this scatter plot we see that the mean of beta 1 hat drastically changes with repect to the increasing value of the true beta 1.  Specifically for the rejected test results, beta 1 hat grew vastly due to the fact that the relationship of beta one and rejectis is the the higher the slope more likely a difference effect of x can be concluded. 
```{r}
overall <- Beat1_data %>%  mutate(beta1 = as.numeric(beta1),
           beta1 = as.factor(beta1),
           null_rejected = case_when(
             pval < 0.05 ~ "reject",
             pval >= 0.05 ~ "fail to reject"
           )
           ) %>% 
    group_by(beta1) %>% 
    summarize(
      mean_beta1 = mean(b1h)
    ) %>% 
  mutate(overall = "overall")

rejected <- Beat1_data %>%  mutate(beta1 = as.numeric(beta1),
           beta1 = as.factor(beta1),
           null_rejected = case_when(
             pval < 0.05 ~ "reject",
             pval >= 0.05 ~ "fail to reject"
           )
           ) %>% 
  filter(pval < 0.05) %>% 
    group_by(beta1) %>%
    summarize(
      mean_beta1 = mean(b1h)
    ) %>% 
  mutate(overall = "rejected")


rbind(overall, rejected) %>% 
  ggplot(aes(x = beta1, y = mean_beta1, col = overall, shape = overall))+
  geom_point(stat = "identity")+
  labs(y = "mean beta 1 hat", legend = NULL)
  ggtitle("Overal Beta1 hat means by True Beta1 Value")
  

```


